### 2015-03-03 ThesisJo/introduction.tex
la2pdf commit - 2015:03:03	11:57:24	(Tue 3.Mar)

@@

@@

where $\nabla^2$ is the Laplacian operator

>>>>

Light fast, sound slow.
Sound propagate far, light attenuated.

@@

When a rock is thrown into a pound of water it abruptly displaces water away from the center of impact. 
%This is an unstable state where various physical phenomena wrestle for control. Gravity wants the water back where it was, inertia cause the mass to resist any change in its state of motion.
This results in spherical waves propagating from the displacement center, transporting the kinetic energy of the rock. These waves are described by how their particles move. At the surface particles will move down up and down, and back and forth, in a circular motion. In the depths particles move longitudinally, transporting energy by means of alternating pressure.

@@

where $\nabla^2$ is the Laplacian operator.

The wave equation constrains the magnitude of the wavenumber,
%
\begin{align*}
\vec k = \frac{\omega}{c} = \frac{2\pi}{\lambda},
\end{align*}
%
so only the direction of $\k$ varies.
